The Legacy of the European Post-Master in Urbanism at TU Delft: A Text Mining Approach

### 2023-07-06 analysis/paper/paper.qmd
Update topic model code

```{r}
topicToFilter <- 6  # you can set this manually ...
# ... or have it selected by a term in the topic name (e.g. 'children')
topicToFilter <- grep('network', topicNames)[1] 
topicThreshold <- 0.2
selectedDocumentIndexes <- which(theta[, topicToFilter] >= topicThreshold)
filteredCorpus <- corpus[selectedDocumentIndexes]
# show length of filtered corpus
filteredCorpus
```

@@

N = 82
topic_prop_per_year <- theta[1:N,]
colnames(topic_prop_per_year) <- topic_names
vizDataFrame <- melt(cbind(data.frame(topic_prop_per_year), 
                           document = factor(rownames(topic_prop_per_year))), 
                     variable.name = "topic", id.vars = "document")

# plot topic proportions per decade as bar plot
vizDataFrameWithYear <- vizDataFrame |> 
  left_join(select(emu_theses, title, graduation_year), by = c("document" = "title")) |> 
  ggplot(aes(x=factor(graduation_year), y=value, fill = topic)) + 
  geom_bar(stat = "identity", position = "fill") +
  scale_fill_viridis_d(name = "Topics") +
  xlab("Graduation year") +
  ylab("Proportion of topics") +
  labs(title = "Proportion of summed topic probabilities over the years of the EMU program")

>>>>

```{r}
topicToFilter <- 6  # you can set this manually ...
# ... or have it selected by a term in the topic name (e.g. 'children')
topicToFilter <- grep('river', topic_names)[1] 
topicThreshold <- 0.2
selectedDocumentIndexes <- which(theta[, topicToFilter] >= topicThreshold)
filteredCorpus <- emu_theses[selectedDocumentIndexes,]
# show length of filtered corpus
filteredCorpus
```

@@

N = 82
topic_prop_per_year <- theta[1:N,]
colnames(topic_prop_per_year) <- topic_names

vizDataFrameWithYear <- melt(cbind(data.frame(topic_prop_per_year), 
                           document = factor(rownames(topic_prop_per_year))), 
                     variable.name = "topic", id.vars = "document") |> 
    left_join(select(emu_theses, title, "year" = graduation_year), by = c("document" = "title"))

# Plot topic proportions per year
vizDataFrameWithYear |> 
  ggplot(aes(x = factor(year), y = value, fill = topic)) + 
  geom_bar(stat = "identity", position = "fill") +
  scale_fill_viridis_d(name = "Topics") +
  xlab("Graduation year") +
  ylab("Proportion of topics") +
  labs(title = "Topic proportions per year")
